\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-06-16 AffineLieAlgebras/InformalNotes/article.tex
Bibliography work, some text on coset construction is partially written.

There exist several approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

@@

The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}. It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.

It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$. It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.

@@

@@

>>>>

There exist several approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

@@

The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}. It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
\begin{comment}
  There exists a classification of modular invariant partition functions for some cases, see . [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
\end{comment}
\begin{comment}
  Formulate this as lemma

It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$. It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
\end{comment}

@@

Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}. Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. The characters of the coset model are connected with the branching functions in the following way:
\begin{equation}
  \label{eq:31}
  \chi
\end{equation}
The problem of the branching functions construction in coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}. The results were mostly given in rather cumbersome form and could not be easily used in computations. The method of calculation of the branching coefficients proposed in this text can be used to get power series expansion of the branching functions up to any required degree. In future work we are going to write complete expansion of the branching functions.

In this section we present the example of the computation of branching functions power series expansion for the embedding $A_1\subset B_2$.

@@

This expansion can be used to compute the conformal dimensions of the primary fields of $B_2/A_1$ coset model in the following way:
\begin{equation}
  \label{eq:35}
  \Delta_{\mu}=
\end{equation}
